%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Kaustav Chanda} \\ \vspace{1pt}
    Senior Software Engineer \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9748802973 ~ \href{mailto:kaustav.chanda.work@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{kaustav.chanda.work@gmail.com}} ~ 
    \href{https://linkedin.com/in/kaustav-chanda}{\raisebox{-0.2\height}\faLinkedin\ \underline{/LinkedIn}}  ~
    \href{https://github.com/kstv364}{\raisebox{-0.2\height}\faGithub\ \underline{/kstv364}} ~
     \href{https://medium.com/@kstvkmrchanda2}{\raisebox{-0.2\height}\faMedium\ \underline{/medium}}  ~
     \href{https://www.hackerrank.com/profile/Kaustav97}{\raisebox{-0.2\height}\faHackerrank\ \underline{/Kaustav97}} ~
    \vspace{-8pt}
\end{center}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Hyland Software}{Oct 2024 -- Present}
      {Developer 2, Content Federation Services}{Kolkata, West Bengal}
      \resumeItemListStart

      \resumeItem{Developed a \textbf{highly scalable WebSocket broker application} to federate \textbf{information exchange} across multiple on-prem content management systems, leveraging a \textbf{plugin-based architecture} for seamless integration and extensibility.}
      
        \resumeItem{Developed a test harness for the above application, as a proxy for \textbf{Amazon API Gateway} reducing endpoint validation time by \textbf{40\%}, enabling faster debugging and integration testing.}

\resumeItem{Refactored a major portion of the \textbf{broker WebSocket application}, improving \textbf{code maintainability} and scalability using \textbf{Factory, Adapter, and Dependency Injection} design patterns.}

\resumeItem{Implemented unit tests covering \textbf{100\% of critical business logic} and achieving \textbf{$>$85\% overall test coverage}, enhancing system reliability and reducing production bugs by \textbf{30\%}.}

\resumeItem{Designed and implemented a \textbf{Proof of Concept (PoC)} for \textbf{streaming large files ($>$20GB) between AWS S3 and on-prem servers}, achieving \textbf{seamless content federation} with a \textbf{20\% improvement in transfer efficiency}.}

\resumeItem{Automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions}, improving deployment frequency by \textbf{3x}, integrating \textbf{SonarCloud scanning}, automated tests, and deployments to \textbf{sandbox and staging environments}.}

      \resumeItemListEnd

    \resumeSubheading
      {Hyland Software}{Feb 2022 -- Sep 2024}
      {Developer 2, Onbase Engineering}{Kolkata, West Bengal}
      \resumeItemListStart
        \resumeItem{Developed \textbf{PDF Support} feature for legacy web based OnBase viewer bringing native PDF functionalities such as \textbf{text-selection, copying text, hyperlink support, bookmark support} generating \textbf{3000+ customer interest points} in Hyland Community.}
        \resumeItem{Modernized development workflow for legacy web application by using \textbf{Typescript} and \textbf{Webpack} tooling promoting \textbf{test-driven-development} approach. }
        \resumeItem{Containerized legacy web application and automated the process of creating \textbf{Docker images} from latest nightly build and continuous deployment using \textbf{Jenkins} reducing build set up time by around \textbf{75\%.} }
        \resumeItem{Utilized \textbf{Jenkins} and \textbf{Vagrant} to provide a continuous integration service in order to automate the entire process of provisioning a virtual machine, installing the latest nightly build and test files, running the tests, generating a report of the results and cleaning up the resources once per day.}
        \resumeItem{Resolved over \textbf{30 accessibility defects} following \textbf{WCAG Conformance} guidelines diverse audiences achieving accessibility backlog reduction by \textbf{13\%. }}
      \resumeItemListEnd

    \resumeSubheading
      {Hyland Software}{Aug 2020 -- Jan 2022}
      {Developer 1, Onbase Engineering}{Kolkata, West Bengal}
      \resumeItemListStart
        \resumeItem{Contributed to the development of Hyland's modern \textbf{Angular} platform for \textbf{OnBase}, creating shareable components supporting text selection, text search, bookmarking capabilities integrated using \textbf{GraphQL} and \textbf{REST} endpoints. }

        \resumeItem{Developed full fledged pre-import \textbf{web-viewer} module for showing preview of documents, supporting page manipuation operations such as \textbf{rotate, reorder, delete} before importing to OnBase.}
        \resumeItem{Integrated \textbf{native desktop functionalities} such as \textbf{scanning} and printing through \textbf{virtual print driver} in web application enabling capturing documents using the above. }
        \resumeItem{Wrote \textbf{UI automation} and \textbf{Unit tests} using \textbf{Protractor}, \textbf{Jest}, \textbf{Selenium} and increased \textbf{code coverage} to impressive \textbf{73\%}. }
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-14pt}

%-----------PROJECTS-----------
\iffalse
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/kstv364/Mango/tree/master}{Food Delivery App}} $|$ \emph{ASP.NET, SqlServer, Docker, Kubernetes }}{December 2023}
          \resumeItemListStart
            \resumeItem{Developed Full-stack Food Delivery App using \textbf{ASP.NET}, \textbf{SQL Server} and \textbf{Entity Framework}. Implemented Authentication and Authorization using \textbf{.NET Identity} and \textbf{Json Web Tokens.} }
            \resumeItem{Implemented \textbf{CRUD REST endpoints} for different micro-services such as /order, /cart, /coupon, etc.   }
            \resumeItem{Containerized the different micro-services using \textbf{Docker compose.} }

          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Signature Capture Module} $|$ \emph{Angular, Jest}}{August 2020}
          \resumeItemListStart
            \resumeItem{Created  Unified Web Based \textbf{E- Signature Capture} Module which supports \textbf{plug-and-play} for third-party signature pad devices such as Wacom, Topaz, etc.}
            \resumeItem{Understood existing {third party SDK’s} and integrated them to fetch captured images from devices.}
            \resumeItem{Used \textbf{Observer} and \textbf{Strategy Design Pattern} to register different signature capture modules with the central signature capture manager. }
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-14pt}
\fi

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, HTML/CSS, Typescript, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Visual Studio, IntelliJ, Git, TFS} \\
     \textbf{Technologies/Frameworks}{: .NET, Linux, Jenkins, Docker, Webpack, Github Actions} \\
    }}
 \end{itemize}
 \vspace{-16pt}

 
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Heritage Institute of Technology (DGPA - 8.95) }{July 2016 -- May 2020}
      {Bachelor of Technology in Computer Science and Engineering} {Kolkata, West Bengal} \\
   
  \resumeSubHeadingListEnd



%-----------INVOLVEMENT---------------
\section{Achievements}
    \resumeItemListStart
        \resumeSubItem{Won the Hyland SPOT award 2021, 2023.}
        \resumeSubItem{NASA Space Apps Challenge 2017 Finalist.}
        \resumeSubItem{School Topper in Mathematics}
   
    \resumeItemListEnd



\end{document}
